---
title: "Assignment 2 Task 1"
author: "Grace Kumaishi"
date: "1/31/2021"
output: 
  html_document:
    theme: darkly
    code_folding: hide
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(shiny)
library(here)
library(janitor)
library(lubridate)
library(tsibble)
library(feasts)
library(slider)

# read in data
willamette_fish <- read.csv(here("data", "willamette_fish_passage.csv")) %>% 
  clean_names()
```

Your group's .Rmd must be customized as follows:
- With a non-default theme (for example using bootstrap themes, with a custom theme, or with a theme from another package)
- With a separate tab for each of the three sections below the Overview (see this section on tabs in RMarkdown: The Definitive Guide by Yihui Xie, J. J. Allaire, and Garrett Grolemund)
- With code folding applied. All code used to wrangle the data and prepare your graphs & tables should be available for us to see if we click on the code buttons (but hide any warnings & messages)
- The document should be cohesive in presentation and communication (e.g. all graphs should use the same theming, consistent color schemes, etc.)

## Overview {.tabset}
- An engaging image (with caption, including photo credit) that is relevant to the dataset
- A brief summary (3 - 4 sentences) of the dataset, and what is included in this “report”
- A map of the fish ladder location (you can make this in R on your own, or include an existing map appropriately licensed, with attribution)
- A professionally formatted data citation
- Remember: All code that you used to wrangle the data and prepare the graphs should be available to see if we click on the Code buttons. 

```{r}
#data wrangling

fish_ts <- willamette_fish %>% 
  mutate(date = mdy(date)) %>% 
  as_tsibble(key = NULL, index = date)

```


### Tab 1 (QS)

```{r}

```

### Tab 2 (GK)

```{r}

```

### Tab 3 (KD)

```{r}

```

